Visual proteomics using whole-lamella 2D template matching

### 2022-03-09 manuscript.tex
Work on creating a nicer montage [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/7e5fee3254041c2c66855e84f72b36c476ba1cb0.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/7e5fee3254041c2c66855e84f72b36c476ba1cb0/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1954684852

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/4e9e2eda33d911a965d898af77d32172b9a3ec9d/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/4e9e2eda33d911a965d898af77d32172b9a3ec9d}{jojoelfe/deco\_lace\_template\_matching\_manuscript@4e9e2ed}
on March 8, 2022.

>>>>

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/7e5fee3254041c2c66855e84f72b36c476ba1cb0/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/7e5fee3254041c2c66855e84f72b36c476ba1cb0}{jojoelfe/deco\_lace\_template\_matching\_manuscript@7e5fee3}
on March 9, 2022.
